---
title: "Assignment B1"
output: github_document
date: "2023-10-31"
---

Here lies the main body of our new function:

```{r}
#' Mean of variables in dataframe
#' 
#' Take the mean of the numerical variables from the original dataframe and return a named list
#'
#' @param dataf a dataframe with some numerical variables. The name dataf is used here to short for dataframe
#' @return a named list with only the mean of numerical variables
#'
library(tidyverse)
mean_dataset <- function(dataf) {
  stopifnot(is.data.frame(dataf))
  return(dataf %>% select(where(is.numeric)) %>% sapply(mean, na.rm = TRUE))
}

```

Here are some examples using this function:
Example 1:
```{r}
mean_dataset(mtcars)
```

Here we shall see that the function produced a named list for all variables in the `mtcars` dataset. Since the dataset `mtcars` has all its variables as numeric variables, the function outputs mean of all variables.

Example 2:
```{r}
head(sleep)
mean_dataset(sleep)
```

As shown in the `sleep` dataset, the factor type variables are not shown in the function output. Only the numeric variables are calculated.

Example 3:
```{r}
factor_dataf <- data.frame(levels = c("High", "Low"), response = c("Well", "Poor"))
mean_dataset(factor_dataf)
```

As shown in the simple`factor_dataf` dataset without any numerical variable, an empty named list will be returned.

Example 4:
```{r, error = TRUE}
mean_dataset(3)
```

As shown in this example, any input not the type of dataframe will cause an error.


Testing:

We would use some tests to varify the function's functionality:

```{r}
library(testthat)

expect_equal(c(passing = 2), mean_dataset(data.frame(passing = c(1,1,3,3))))
expect_equal(c(passing = 2), mean_dataset(data.frame(passing = c(1,2, NA, 3))))
expect_equal(c(passing = 2), mean_dataset(data.frame(passing = c(1,1,3,3), frac = c("First", "Second", "Third", "Fourth"))))
expect_error(mean_dataset("545B"))
expect_length(mean_dataset(data.frame(passing = c())),0)

```

